% FACTORIE User's Guide
% Copyright (c) 2009-. University of Massachusets, Department of Computer Science.
% Released under the Creative Commons 3.0 BY License.

%
% This manual is currently unfinished.  
% When it has more useful content, it will be directly linked from the
% FACTORIE web site.
%



\documentclass[]{manual}

% Use utf-8 encoding for foreign characters
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage[bitstream-charter]{mathdesign}

% Setup for fullpage use
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{epsfig}
\usepackage{color}
%\usepackage{pdfsync}

% Flexible citation syntax
\usepackage{natbib}

% Multipart figures
%\usepackage{subfigure}

% More symbols
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{latexsym}

% Line numbering
\usepackage{lineno}

% Package for including code in the document
\usepackage{listings}

% Surround parts of graphics with box
\usepackage{boxedminipage}

\usepackage{upquote}

% This is now the recommended way for checking for PDFLaTeX:
%\usepackage{ifpdf}

% Enable hyperlinks
\definecolor{Red}{rgb}{0.5,0,0}
\definecolor{Blue}{rgb}{0,0,0.5}
\usepackage[pdfpagemode=FullScreen,colorlinks=true,linkcolor=Red,citecolor=Blue,urlcolor=Red]{hyperref}

%\ifpdf
%\usepackage[pdftex]{graphicx}
%\else
%\usepackage{graphicx}
%\fi


\title{FACTORIE User's Guide:\\
Probabilistic Programming via Imperatively Defined Factor Graphs}
\author{Andrew McCallum \\ Karl Schultz \\ Sameer Singh \\ Sebastian Riedel \\ Michael Wick}
\graphicspath{{figs/}}
\pdfoutput=1
%\release{0.8}
%\date


%%%%%%%%%%%%%%% Commands from rst2latex %%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\rubric}[1]{\subsection{#1}}
\newcommand{\titlereference}[1]{\textsl{#1}}
\newlength{\locallinewidth}
\setlength{\locallinewidth}{7in}
\newlength{\admonitionwidth}
\setlength{\admonitionwidth}{0.9\textwidth}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{secnumdepth}{1}


\begin{document}

\maketitle

\tableofcontents
%\linenumbers

% Examples to consider including:
% <h2>Coin Flips</h2>
% <h2>Rain, Sprinkler and Wet Grass</h2>
% <h2>Document Clustering with a Mixture of Multinomials</h2>
% <h2>Latent Dirichlet Allocation</h2>
% <h2>Smoking, Cancer and Friendships</h2>
% <h2>Companies, Employers and Respect</h2>
% <h2>Named Entity Recognition with Linear-chain CRFs</h2>
% <h2>Entity Resolution</h2>
% <h2>Dependency Parsing</h2>

\chapter{Introduction}
\label{chap:intro}

An overview of FACTORIE and its features.

\chapter{Installation}
\label{chap:install}

Where to find FACTORIE.  How to install it.  Where to find updates.
Where to find other users, discussion groups.  How to report errors
and suggestions.


\chapter{Tutorial}
\label{chap:tutorial}

A tutorial, based on multiple examples.  Show examples of
entity-relationship style of template definition, logic syntactic
sugar, and underlying imperative style.  Show examples of both
undirected and directed models.


\chapter{Variables and Domains}
\label{chap:variables}

Objects representing random variables.

\section{The Basic Variable Classes}
\section{Defining Your own Variable Classes}
\section{Defining a Variable's Domain}
\section{Variables of Generative Models}
\section{Generative Distributions}


\chapter{Defining Models with Factor Templates}
\label{chap:models}


\chapter{Inference}
\label{chap:inference}

Sampling, MCMC, variational, maximization.


\chapter{Learning}
\label{chap:learning}

Objective functions as models.


\chapter{Diagnostics}
\label{chap:diagnostics}

\chapter{Database Back-end}
\label{chap:database}

\chapter{Conclusion}
\label{chap:conclusion}


% \appendix
% \chapter{Appendix: Foo}

\bibliographystyle{plainnat}
\bibliography{factorie-users-guide}

\end{document}
